A Structural and Functional Bioinformatics Study of QTY-designed Retinylidene Proteins

### 2025-05-15 Paper/Manuscript/manuscript.tex
Reorganize paper latex files for QRB Discovery Submission.
Submit to QRB D.

\keywords{hydrophobic to hydrophilic conversion; membrane proteins; protein design; QTY code; water-soluble retinylidene proteins; water-soluble opsins; activation of QTY variants of rhodopsin}
\begin{abstract}

@@

There is no financial support for this digital bioinformatics study. We only used free tools that are publicly available.

@@

Massachusetts Institute of Technology (MIT) filed several patent applications for the QTY code for GPCRs excluding the human opsins. OH2Laboratories licensed the technology from MIT to work on water-soluble GPCR variants. S.Z. is an inventor of the QTY code and has a minor equity in OH2Laboratories. S.Z. is a Scientific Advisor and has minor shares for a startup RealNose to develop a sensing device based on olfactory receptors. S.Z. founded a startup 511 Therapeutics to generate therapeutic monoclonal antibodies against solute carrier transporters to treat pancreatic cancer. S.Z. has majority equity in 511 Therapeutics. All other authors have no competing interests.

>>>>

\keywords{bioinformatics; computational studies on functional properties of biological molecule; GPCRs; membrane protein structure; protein dynamics simulation}
\begin{abstract}

@@

There is no financial support for this digital bioinformatics study. I only used free tools that are publicly available.

@@

Massachusetts Institute of Technology (MIT) filed several patent applications for the QTY code for GPCRs, which do not include the human opsins. There are no competing interests.
